Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-12-23 main.tex
done editing Sec. V-B

\subsection{Results in a static setting} % \skug{Full: 3, Polished: 2}}
\label{sec.expe.static}

   % \subsubsection{Preliminary experiments}
We first study the heuristics behavior when the weights do not change upon runtime,
hence the scheduler has a perfect knowledge of task memory requirements and execution times.
We have compared two eviction strategies, starting with large files first or small files first,
and did not report any significant changes in terms of validity of schedule or makespan.
Hence, we only present results with the eviction of largest files first.
%    Our preliminary experiments have shown that evicting large or small files does not give a notable change in makespan.

    \subsubsection{Scheduling on the default cluster}

%    \paragraph{Normal cluster}

    On the default cluster,  the three memory-aware heuristics are able to schedule all workflows
    (see Figure~\ref{fig:success-rates-large}), while
    the baseline \heft has $24.2\%$ success rate ($75.7\%$ failure rate).
    Indeed, \heft is only able to schedule small workflows, but no workflow over the size of $4000$ tasks
    can be scheduled correctly; some tasks run out of memory. As soon as we are not in a setting
    with abundant processing resources for small workflows, it is hence necessary to adopt
    a memory-aware strategy in order to produce valid schedules.
%    Small workflows are less constrained by the memory requirement, so in the situation of abundant processing resources, even
%    a not memory-aware approach is able to produce valid schedules.
%    However, this advantage quickly vanishes as workflows grow larger.

    \begin{figure}[tb]
        \centering
        \includegraphics[width=0.99\columnwidth] {images/success-rates-large}
        \caption{Success rates on the default cluster. Higher is better.}
        \label{fig:success-rates-large}
        \vspace{-0.3cm}
    \end{figure}

   We also report in  Figure~\ref{fig:ms-relations-by-workflow}  the relative makespan found
   by the memory-aware heuristics, normalized to the
   makespan achieved by \heft, often through an invalid over-optimistic schedule that exceeds
   the bound on memory.
%    Figure~\ref{fig:ms-relations-by-workflow} shows the relations of the makespans found by the heuristics to the
%    makespans found by the baseline (including invalid ones), by workflow size.
    On average, the makespans found by \heftbl are $7.8\%$ worse than those found by the baseline,
    the makespans of \heftblc are $8\%$
    worse, and those found by \heftmm are $82.6\%$ worse. These are still very encouraging results,
    in particular for \heftbl and \heftblc, since the makespans of \heft correspond to invalid schedules.

@@

    Finally, we study the percentage of memory occupied by the schedule, which is another good indicator
    of the memory usage of the heuristic and its ability to produce valid schedules.  %its important characteristic.
    Figures \ref{fig:mem-usages-normal} and~\ref{fig:mem-usages-onlyvalid} show the percentage of memory
    occupied on average by the schedule
    produced by the different heuristics, for different workflow sizes, first on all schedules (hence including
    \heft schedules that were not valid), and then only on valid schedules (hence, no results for \heft
    on large workflow sizes).
%
%   Figure shows memory usages if only valid heft schedules are presented.
%    There are no valid heft scheduler from middle-sized and large workflows, so no red bars are present.

    \heftmm continuously outperforms other heuristics in terms of memory usage,
    using from $46\%$ less memory on the smallest
    workflows to $4$ times less memory on the largest \numprint{30000}-task workflows.
    If we consider the invalid \heft schedules, too, we see that they would require more and more memory on average,
    which explains why these schedules rapidly become invalid.
    This is because some assignments require more that $100\%$ of memory (which makes them invalid).
    We can assess the degree of invalidity by comparing \heft memory usage with the memory usage of \heftbl.
    \heftbl differs from the baseline only in the sense that it respects available memory on the processors.
    For the largest workflows, \heft schedules require almost twice the memory of \heftbl.

@@

\subsubsection{Scheduling on the memory-constrained cluster}

    On the memory-constrained cluster, \heft could produce valid assignments in only $14$ experiments
    out of $290$~($4.8\%$ success rate).
    The successful schedules were achieved exclusively on the tiny workflows (with only two 200-task size-increased
    workflow among them).
    \heftbl could successfully schedule $38\%$ of workflows, \heftblc could schedule $49\%$ of them, while \heftmm
    could still schedule all the workflows, including even the largest ones, see Figure~\ref{fig:success-rates-tiny}.
    As also observed on the normal cluster, \heftmm seems to be less affected by the size of the workflow
    when scheduling it than the other heuristics.

    Similarly to the default cluster, we observe that relative makespan of \heftmm is usually greater
    than those of \heft (see Fig.~\ref{fig:ms-relations-by-workflow-constrained}), but \heft schedules are
    almost all invalid. It is therefore very interesting to resort to \heftmm for large workflows
    in a constrained cluster, since tasks are processed in an order that minimizes
    the memory usage of schedule.
%
%    The makespans it produces are larger, but it seems to order the vertices in a similar way on both the small and the large workflows,
%    rather than resorting to more memory-consuming ordering that other heuristics and the baseline produces.
%    This makes it especially valuable for very large workflows in situations of very constrained memory in the cluster.
%
%

>>>>

\subsection{Results in a static setting}
\label{sec.expe.static}
%
We first study the heuristics' behavior when the weights do not change during runtime,
hence the scheduler has perfect knowledge of the task memory requirements and execution times.
We have compared two eviction strategies, starting with large files first or small files first,
and did not observe any significant changes in terms of schedule validity or makespan.
Thus, we only present results with the eviction of largest files. % first. TODO: Why ``first''?
%    Our preliminary experiments have shown that evicting large or small files does not give a notable change in makespan.

\subsubsection{Scheduling on the default cluster}
%
%    \paragraph{Normal cluster}
%
On the default cluster,  the three memory-aware heuristics are able to schedule all workflows
(see Figure~\ref{fig:success-rates-large}), while
the baseline \heft has a success rate of only $24.2\%$ ($75.7\%$ failure rate).
Indeed, \heft is only able to schedule small workflows; it cannot schedule any workflow 
with more than $4000$ tasks correctly as some tasks run out of memory. As soon as we are not in a setting
with abundant processing resources for small workflows, it is hence necessary to adopt
a memory-aware strategy in order to produce valid schedules.
%    Small workflows are less constrained by the memory requirement, so in the situation of abundant processing resources, even
%    a not memory-aware approach is able to produce valid schedules.
%    However, this advantage quickly vanishes as workflows grow larger.

\begin{figure}[tb]
  \centering
  \includegraphics[width=1\columnwidth] {images/success-rates-large}
  \caption{Success rates on the default cluster. Higher is better.}
  \label{fig:success-rates-large}
  \vspace{-0.3cm}
\end{figure}

We also report in  Figure~\ref{fig:ms-relations-by-workflow} the relative makespan found
by the memory-aware heuristics, normalized to the
makespan achieved by \heft, often with an invalid over-optimistic schedule that exceeds
the bound on memory.
%    Figure~\ref{fig:ms-relations-by-workflow} shows the relations of the makespans found by the heuristics to the
%    makespans found by the baseline (including invalid ones), by workflow size.
On average, the makespans found by \heftbl are $7.8\%$ worse than those found by the baseline,
the makespans of \heftblc are $8.0\%$
worse, and those found by \heftmm are $82.6\%$ worse. These are still very encouraging results,
in particular for \heftbl and \heftblc, since the makespans of \heft correspond to invalid schedules.

@@

Finally, we study the percentage of memory occupied by the schedule, which is another good indicator
of the memory usage of the heuristics and their ability to produce valid schedules.  %its important characteristic.
Figures \ref{fig:mem-usages-normal} and~\ref{fig:mem-usages-onlyvalid} show the percentage of memory
occupied on average by the schedule
produced by the different heuristics for different workflow sizes;
first on all schedules (including invalid \heft schedules) and then only on 
valid schedules (hence, no results for \heft on large workflow sizes).
%
%   Figure shows memory usages if only valid heft schedules are presented.
%    There are no valid heft scheduler from middle-sized and large workflows, so no red bars are present.

\heftmm continuously outperforms the other heuristics in terms of memory usage,
using from $46\%$ less memory on the smallest
workflows to $4$ times less memory on the largest ones with \numprint{30000} tasks.
If we consider the invalid \heft schedules, too, we see that they would require more and more memory on average,
which explains why these schedules rapidly become invalid.
This is because some assignments require more than $100\%$ of the memory (which makes them invalid).
We can assess the degree of invalidity by comparing \heft memory usage with the memory usage of \heftbl.
\heftbl differs from the baseline only in the sense that it respects the available memory on the processors.
For the largest workflows, \heft schedules require almost twice as much memory as \heftbl.

@@

\subsubsection{Scheduling on the memory-constrained cluster}
\label{ss:mem-constrained-cluster}
%
On the memory-constrained cluster, \heft produces valid assignments in only $14$ out of $290$ experiments
$290$~($4.8\%$ success rate).
The successful schedules are achieved exclusively on the tiny workflows (with only two 200-task size-increased
workflow among them).
\heftbl successfully schedules $38\%$ of the workflows, \heftblc is able to schedule $49\%$ of them, while \heftmm
still schedules all of them, including even the largest ones, see Figure~\ref{fig:success-rates-tiny}.
As also observed on the default cluster, \heftmm seems to be less affected by the workflow size
than the other heuristics.

Similarly to the default cluster, we observe that the makespan of \heftmm is usually higher
than with \heft (see Fig.~\ref{fig:ms-relations-by-workflow-constrained}), but the \heft schedules are
almost all invalid. It is thus worthwhile to resort to \heftmm for large workflows
in a constrained cluster, since tasks are processed in an order that minimizes
the memory usage of schedule.
%
%    The makespans it produces are larger, but it seems to order the vertices in a similar way on both the small and the large workflows,
%    rather than resorting to more memory-consuming ordering that other heuristics and the baseline produces.
%    This makes it especially valuable for very large workflows in situations of very constrained memory in the cluster.
%
%
